ScPy: A SuperCollider Extension for Perforeing Numerical Computation via Embedded Python

### 2016-08-24 doc/paper.tex
write about the list/array conversion stuff

@@

\title{ScPy: A SuperCollider Extension for Performing Numerical Computation via Embedded Python}

@@

When listing \ref{lst:boilerplate} is run, an anonymous synth is created which will take in audio
from an external source, perform a STFT, process the spectral data with ScPy, perform an inverse
STFT, then finally output the resulting audio. Lines 8-9 contain Python code defining the
processing function where operations are to be inserted. Further examples will replace only those
lines. Line 16 contains the Python code to convert the spectrum into a NumPy array, process it,
then write back the processed version.

@@

\begin{table}[H]
    \caption{Type correspondence between SuperCollider and Python}
    \begin{center}
        \begin{tabular}{| l | l |}
            \hline
            SuperCollider data type & Python data type \\ \hline
            \texttt{Float} & \texttt{float} \\ \hline
            \texttt{UGen} & \texttt{ndarray} of \texttt{float} \\ \hline
            \texttt{Buffer} & \texttt{ndarray} of \texttt{float} \\ \hline
            \texttt{FFT} & \texttt{ndarray} of \texttt{complex} \\ \hline
            \texttt{Array} & \texttt{list} \\ \hline
        \end{tabular}
    \end{center}
\end{table}

>>>>

\providecommand*{\listingautorefname}{Listing}

@@

\title{ScPy: A SuperCollider Extension for Perforeing Numerical Computation via Embedded Python}

@@

When \autoref{lst:boilerplate} is run, an anonymous synth is created which will take in audio
from an external source, perform a STFT, process the spectral data with ScPy, perform an inverse
STFT, then finally output the resulting audio. Lines 8-9 contain Python code defining the
processing function where operations are to be inserted. Further examples will replace only those
lines. Line 16 contains the Python code to convert the spectrum into a NumPy array, process it,
then write back the processed version.

@@

Since \texttt{FFT} objects in SuperCollider operate on a single channel only, they must be placed
in \texttt{Array} objects to support multichannel audio. \texttt{Array}s can hold objects of any
type, so it is natural to convert them to Python \texttt{list} objects, which have similar
properties. However, this presents an interesting problem: multichannel \texttt{FFT} objects are
then converted to \texttt{lists} of \texttt{ndarray} objects in Python. These are a bit more
awkward to work with than basic \texttt{ndarray} objects, but can easily be converted using a call
to the \texttt{array} function in Python. This can be seen in practice on line 16 of
\autoref{lst:boilerplate}. Although it would be possible to do this conversion
automatically, it is left out for the purpose of not introducing a feature simply to work around an
incomplete implementation of \texttt{FFT} objects in SuperCollider. The current conversions will
continue to function as intended if \texttt{FFT} objects are given multichannel support in the
future.

\begin{table}[H]
    \caption{Type correspondence between SuperCollider and Python}
    \begin{center}
        \begin{tabular}{| l | l |}
            \hline
            SuperCollider data type & Python data type \\ \hline
            \texttt{Float} & \texttt{float} \\ \hline
            \texttt{UGen} (subclass of) & \texttt{ndarray} of \texttt{float} \\ \hline
            \texttt{Buffer} & \texttt{ndarray} of \texttt{float} \\ \hline
            \texttt{FFT} & \texttt{ndarray} of \texttt{complex} \\ \hline
            \texttt{Array} & \texttt{list} \\ \hline
        \end{tabular}
    \end{center}
\end{table}
